Create Label Density

### 2022-02-16 eda/calculate_label_density.Rmd
change col name

top <- labeled_amicus %>% 
  filter(excerpt_divided_if_yes_top_or_bottom_coded %in% c("top", "all(short)")) %>% 
  select(case:fem, -text, text = divided_1, hm_label_code_s)

bottom <- labeled_amicus %>% 
  filter(excerpt_divided_if_yes_top_or_bottom_coded == "bottom") %>% 
  select(case:fem, -text, text = divided_2, hm_label_code_s)

not_div <- labeled_amicus %>% 
  filter(excerpt_divided_if_yes_top_or_bottom_coded == "not divided") %>% 
  select(case:fem, hm_label_code_s)

>>>>

top <- labeled_amicus %>% 
  filter(excerpt_divided_if_yes_top_or_bottom_coded %in% c("top", "all(short)")) %>% 
  select(case:fem, -text, text = divided_1, label = hm_label_code_s)

bottom <- labeled_amicus %>% 
  filter(excerpt_divided_if_yes_top_or_bottom_coded == "bottom") %>% 
  select(case:fem, -text, text = divided_2, label = hm_label_code_s)

not_div <- labeled_amicus %>% 
  filter(excerpt_divided_if_yes_top_or_bottom_coded == "not divided") %>% 
  select(case:fem, label = hm_label_code_s)
